Binning Strategies and Related Loss for Large Data

### 2015-03-09 Paper.Rnw
Add figure to frequency loss section

>>>>

<<FreqLossDemo,echo=F,include=T,eval=T,fig.width=6, fig.height=3, out.width='.8\\linewidth', fig.pos='H',fig.align='center',tidy=F, cache=TRUE, fig.show='hold'>>= 
library(ggplot2)
library(gridExtra)
J = 0.01
J2 = 200
bound = 1000
id <- seq(0+J/2,bound-J/2,by=J )
fill <- seq(0+J/2,bound-J/2,by=J )
id2 <- seq(0+J2/2,bound-J2/2, by=J2)
fill2 <- seq(J2/2,bound-(J2/2), by=J2)
p1 <- qplot(id, 2, geom="tile", fill=-fill) +
  theme(plot.margin = unit(c(0.1,1,0.1, 1),"cm"), 
        legend.position = "none",
        axis.ticks=element_blank(),
        axis.text.y=element_blank(),
        panel.background=element_blank()
        ) + 
  ylab("Continuous") + xlab("")
p2 <- qplot(id2, 2, geom="tile", fill=-fill2) + 
  theme(plot.margin = unit(c(0.1,1,0.1, 1),"cm"), 
        legend.position = "none",
        axis.ticks=element_blank(),
        axis.text.y=element_blank(),
        panel.background=element_blank()) + 
  ylab("Discrete") + xlab("Count")
grid.arrange(p1,p2,nrow=2)
#ggsave("./figure/FreqBin.pdf",width=5, height=1.5)
@
